MLH1 Results Outline

### 2020-04-23 doc/Results_v2.rmd
working on the triangle plots

@@

#remove grey background
#add diagonal
#

IFD.Male.DOM.top.tri.plot <- ggplot( (Curated_BivData %>% filter(sex == "male") %>% filter(hand.foci.count == 2) %>% filter(subsp == "Dom") ),
  aes(y = rev(PER_Foci_2), x= PER_Foci_1, color=strain))+
  geom_jitter(alpha=.4)+
  ggtitle("Normalized IFD\nDom")+
  scale_color_manual(values=colors_of_strains)+xlim(c(0,1))+ylim(c(0,1))+
  theme(legend.position="none")+theme_classic()+geom_abline(intercept = 0, slope = 1)

IFD.Male.DOM.tri.plot

basey.base <- plot( y = (Curated_BivData %>% filter(sex == "male") %>% filter(hand.foci.count == 2) %>% filter(subsp == "Dom") )$PER_Foci_2, x= (Curated_BivData %>% filter(sex == "male") %>% filter(hand.foci.count == 2) %>% filter(subsp == "Dom") )$PER_Foci_1 )

>>>>

```{r Q1.ggplot_IFD.triangle, echo=FALSE}
#IFD.Male.DOM.top.tri.plot <- ggplot( (Curated_BivData %>% filter(sex == "male") %>% filter(hand.foci.count == 2) %>% filter(subsp == "Dom") ),
#  aes(y = rev(PER_Foci_2), x= PER_Foci_1, color=strain))+
#  geom_jitter(alpha=.4)+
#  ggtitle("Normalized IFD\nDom")+
#  scale_color_manual(values=colors_of_strains)+xlim(c(0,1))+ylim(c(0,1))+
#  theme(legend.position="none")+theme_classic()+geom_abline(intercept = 0, slope = 1)

```{r with.cow, echo=FALSE, warning=FALSE}
library(cowplot)

top.triangle <- function() {
  plot( PER_Foci_2 ~ PER_Foci_1, data = (Curated_BivData %>% filter(sex == "female") %>% filter(hand.foci.count == 2) %>% filter(subsp == "Dom") ), 
      axes = FALSE, ylab = 'Foci2', xlab = NA, main='Foci1',
      xlim=c(0,1), ylim=c(0,1),  xaxt="n", yaxt="n" )
  axis(side = 2, las = 1, pos=0)
  axis(side = 3, las = 1, pos=1)
  abline(coef = c(0,1))

}

bottom.triangle <- function() {
  plot( PER_Foci_1 ~ PER_Foci_2, data = (Curated_BivData %>% filter(sex == "female") %>% filter(hand.foci.count == 2) %>% filter(subsp == "Dom") ), 
      axes = FALSE, xlab = NA, ylab = NA, xlim=c(0,1), ylim=c(0,1),  xaxt="n", yaxt="n" )
  axis(side = 1, las = 1, pos=0)
  axis(4, las = 1, pos=1) #flip label to right side
  abline(coef = c(0,1))
}

#plot_grid(top.triangle, bottom.triangle, ncol=1)

plot_grid(top.triangle, bottom.triangle, align = "v", rel_widths = c(1.3, 1.3))

@@

#remove grey background
#add diagona

#trying with base R

plot( PER_Foci_2 ~ PER_Foci_1, data = (Curated_BivData %>% filter(sex == "female") %>% filter(hand.foci.count == 2) %>% filter(subsp == "Dom") ), 
      axes = FALSE, ylab = 'Foci2', xlab = NA, main='Foci1',
      xlim=c(0,1), ylim=c(0,1),  xaxt="n", yaxt="n" )

axis(side = 2, las = 1, pos=0)
axis(side = 3, las = 1, pos=1)
abline(coef = c(0,1))

#bottom triangle, Female
plot( PER_Foci_1 ~ PER_Foci_2, data = (Curated_BivData %>% filter(sex == "female") %>% filter(hand.foci.count == 2) %>% filter(subsp == "Dom") ), 
      axes = FALSE, xlab = NA, ylab = NA, xlim=c(0,1), ylim=c(0,1),  xaxt="n", yaxt="n" )
axis(side = 1, las = 1, pos=0)
axis(4, las = 1, pos=1) #flip label to right side
abline(coef = c(0,1))

#use cowplot or another way to paste these together
